### 2021-07-03 docs/manuscript/manuscript.tex
Extend discussion on robustness and connectivity

Robustness is an important feature of patterning mediated by morphogens, and
the GRNs involved can be selected in an evolutionary process not only by their final
steady state but also by their ability to buffer noise~\cite{lo_robust_2015, exelby_2021}.
In our study, the most abundant topologies were
found to be part of highly connected clusters in the neutral network, and this fact
indicates that these topologies are both robust to quantitative changes in the
strength of interactions and diffusion and degradation parameters as well as to
qualitative changes in the topology itself. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable.\\

>>>>

Robustness is an important feature of patterning mediated by morphogens, and
the GRNs involved can be selected in an evolutionary process not only by their final
steady state but also by their ability to buffer noise~\cite{lo_robust_2015, exelby_2021}.
In our study, the most abundant topologies were
found to be part of highly connected clusters in the neutral network, and this fact
indicates that these topologies are both robust to quantitative changes in the
strength of interactions and diffusion and degradation parameters as well as to
qualitative changes in the topology itself. This, in principle, means that many
mechanisms for producing striped patterns are available and accessible to each
other, i.e., an organism can change between different GRNs without losing its
fitness, which allows to fine-tune the regulatory system according to its specific
needs. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable in the sense that they can produce
heritable variation of the expression pattern.\\
